\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-03-26 doc/sw-system.tex
Now up to section 5... #96

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_histories.png}
\caption{Typical \SW Agent histories. The ``skill'' of the  same 200 random
Agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
of the number  of subjects classified (``effort''). The yellow histogram in
the background shows the distribution of effort.}
\label{fig:swap:agent-histories}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_trajectories.png}
\caption{Typical \SW \StageOne subject trajectories. Subjects drift downwards in
the top panel as they are classified, while being nudged left and right by the
Agents as they interpret the volunteers input. The dotted vertical lines show
(left to right) the retirement threshold, prior probability, and the detection
threshold.}
\label{fig:swap:subject-trajectories}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

During \StageOne classification of the CFHTLS images, we assigned a prior
probability for each image to contain a lens of $2\times10^{-4}$, based on a
rough estimate of the number of expected lenses in the survey. We then
assigned two values of the images' posterior probability, $\pr(\LENS|C,T)$, to
define ``detection'' and ``rejection'' thresholds. These were set to be 0.95
and (approximately symmetrically in the logarithm of probability), $10^{-7}$.
Subjects that attained probability of less than the rejection threshold were
scheduled for retirement and subsequently ignored by the analysis code.
Subjects crossing the detection threshold were not retired from the website,
but instead left in the system so that more volunteers could see them. The
progress of the subjects is illustrated in \Fref{fig:swap:subject-trajectories}.
Subjects appear on this plot at the tip of the arrow, at zero classifications
and prior probability; they then drift downwards as they are classified by the
crowd, with each Agent applying the appropriate kick in probability based on
what it hears its volunteer say. Encouragingly, sims (blue) tend to end up
with high probability, while duds (red) pile up at low probability; test
subjects (black) mostly drift to low probability, but some go the other way.
The latter will help make up the candidate sample. As this plot shows, around
10 classifications are required for a subject to reach the retirement
threshold.

@@

When all the subjects had either been retired, or classified around 10 times
or more, the web app was paused and reconfigured for \StageTwo. The sample of
subjects classified during \StageTwo was selected to be all those that passed
the detection threshold ($\pr(\LENS|C,T) > 0.95$) at \StageOne. These were
classified for one week, with no retirement but a maximum classification
number of 50 each. The number of subjects at \StageTwo was small enough that we
did not need to retire any: instead, we simply collected classifications for a
fixed period of time (about 4 weeks). Without the time pressure motivating the
online analysis, we implemented an ``offline'' version of the analysis that
performs a joint inference of all Agent confusion matrix elements and subject
probabilities simultaneously, for comparison. We describe how this differs
from the online analysis in the appendix.

@@

The probabilistic model described above does not need to be implemented as an
online inference. Indeed, it might be more appropriate to perform the inference
of all Agent confusion matrix elements and Subject probabilities
simultaneously, so that the early classifications are not effectively
downweighted as a result of the Agent's ignorance. It might also be that this
ignorance builds in some conservatism to the system, reducing the noise due
the early classifications if they are unreliable. In the joint analysis, the
basic assumption that is built into the Agents, that their volunteers
have innate and unchanging talent for lens spotting parameterised by two
constant confusion matrix elements which simply need to be inferred given the
data, is implemented in full. The effect is that of applying the time-averaged
confusion matrices, rather than one that evolves as the Agents (and in the
real world, the volunteers) learn.

The mathematics of the offline inference are presented elsewhere (in
preparation). Here we briefly note that we maximize the joint posterior
probability distribution for all the model parameters (some 66,000 confusion
matrix elements and 430,000 subject probabilities) with a simple
expectation-maximisation algorithm. This procedure takes approximately the
same CPU time as the \StageTwo online analysis, because no matrix inversions are
required in the algorithm. The algorithm scales well and is actually faster
than the online analysis with the larger \StageOne dataset. The
expectation-maximisation algorithm is robust to initial starting parameters
in, e.g., initial Agent confusion matrix elements and Subject probabilities.
The plots in \Sref{sec:results:sample} show the difference in performance
between the online and offline analyses.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_histories.png}
\caption{Typical \SW Agent histories. The ``skill'' of the  same 200 random
agents  as in \Fref{fig:swap:agent-probabilities} is plotted in green as a function
of the number  of subjects classified (``effort''). The yellow histogram in
the background shows the distribution of effort.}
\label{fig:swap:agent-histories}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_trajectories.png}
\caption{Typical \SW \StageOne subject trajectories. Subjects drift downwards in
the top panel as they are classified, while being nudged left and right by the
agents as they interpret the volunteers input. The dotted vertical lines show
(left to right) the retirement threshold, prior probability, and the detection
threshold.}
\label{fig:swap:subject-trajectories}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

During \StageOne classification of the CFHTLS images, we assigned a prior
probability for each image to contain a lens of $2\times10^{-4}$, based on a
rough estimate of the number of expected lenses in the survey, and the fraction
of the survey area covered by each image. We then assigned two values of the
images' posterior probability, $\pr(\LENS|C,T)$, to define ``detection'' and
``rejection'' thresholds. These were set to be 0.95 and (approximately
symmetrically in the logarithm of probability), $10^{-7}$. Subjects that
attained probability of less than the rejection threshold were scheduled for
retirement and subsequently ignored by the analysis code. Subjects crossing the
detection threshold were not retired from the website, but instead left in the
system so that more volunteers could see them (and continue to update their
probabilities). The progress of the subjects is illustrated in
\Fref{fig:swap:subject-trajectories}. Subjects appear on this plot at the tip of
the arrow, at zero classifications and prior probability; they then drift
downwards as they are classified by the crowd, with each agent applying the
appropriate kick in probability based on what it hears its volunteer say.
Encouragingly, sims (blue) tend to end up with high probability, while duds
(red) pile up at low probability; test subjects (black) mostly drift to low
probability, but some go the other way. The latter will help make up the
candidate sample. As this plot shows, around 10 classifications are typically required for a subject to reach the retirement (or detection) threshold.

@@

When all the subjects had either been retired, or classified around 10 times
or more, the web app was paused and reconfigured for \StageTwo. The sample of
subjects classified during \StageTwo was selected to be all those that passed
the detection threshold ($\pr(\LENS|C,T) > 0.95$) at \StageOne. These were
classified for one week, with no retirement but a maximum classification
number of 50 each. The number of subjects at \StageTwo was small enough that we
did not need to retire any: instead, we simply collected classifications for a
fixed period of time (about 4 weeks). Without the time pressure motivating the
online analysis, we implemented an ``offline'' version of the analysis that
performs a joint inference of all agent confusion matrix elements and subject
probabilities simultaneously, for comparison. We describe how this differs
from the online analysis in the appendix.

@@

The probabilistic model described above does not need to be implemented as an
online inference. Indeed, it might be more appropriate to perform the inference
of all agent confusion matrix elements and Subject probabilities
simultaneously, so that the early classifications are not effectively
downweighted as a result of the agent's ignorance. It might also be that this
ignorance builds in some conservatism to the system, reducing the noise due
the early classifications if they are unreliable. In the joint analysis, the
basic assumption that is built into the agents, that their volunteers
have innate and unchanging talent for lens spotting parameterised by two
constant confusion matrix elements which simply need to be inferred given the
data, is implemented in full. The effect is that of applying the time-averaged
confusion matrices, rather than one that evolves as the agents (and in the
real world, the volunteers) learn.

The mathematics of the offline inference are presented elsewhere (in
preparation). Here we briefly note that we maximize the joint posterior
probability distribution for all the model parameters (some 66,000 confusion
matrix elements and 430,000 subject probabilities) with a simple
expectation-maximisation algorithm. This procedure takes approximately the
same CPU time as the \StageTwo online analysis, because no matrix inversions are
required in the algorithm. The algorithm scales well and is actually faster
than the online analysis with the larger \StageOne dataset. The
expectation-maximisation algorithm is robust to initial starting parameters
in, e.g., initial agent confusion matrix elements and Subject probabilities.
The plots in \Sref{sec:results:sample} show the difference in performance
between the online and offline analyses.
